Preliminary Experiment

### 2018-03-16 preliminary/preliminary_report.tex
another typo

$N = 200$ simulations were run. \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Needle-in-haystack
\begin{enumerate}
\item High (with three arms) - 2 arms with mean 0.50, 1 arm with mean 0.7 (+ 0.2)
\item High (with ten arms) - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\item Medium-High (with ten arms) - 8 arms with mean 0.50, 1 arm with 0.60, 1 arm 0.80
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon = 0.05$
\item Non-Bayesian $\epsilon$-greedy - the greedy decision was made based on empirical mean. When there were zero observations, assumed that the empirical mean was 0 (this seems questionable), $\epsilon = 0.05$
\item UCB1 (with constant $1$)
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each experiment $i$}
		\State Use $p$ as the true distribution of the arms
		\State Generate realizations for each arm and round $t$ and instantiate bandit instance
		\For{Each algorithm $alg$}
			\State Run simulation for $T$ periods
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

$N = 200$ simulations were run. \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Needle-in-haystack
\begin{enumerate}
\item High (with three arms) - 2 arms with mean 0.50, 1 arm with mean 0.7 (+ 0.2)
\item High (with twenty arms) - 19 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\item Medium-High (with twenty arms) - 18 arms with mean 0.50, 1 arm with 0.60, 1 arm 0.80
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon = 0.05$
\item Non-Bayesian $\epsilon$-greedy - the greedy decision was made based on empirical mean. When there were zero observations, assumed that the empirical mean was 0 (this seems questionable), $\epsilon = 0.05$
\item UCB1 (with constant $1$)
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each experiment $i$}
		\State Use $p$ as the true distribution of the arms
		\State Generate realizations for each arm and round $t$ and instantiate bandit instance
		\For{Each algorithm $alg$}
			\State Run simulation for $T$ periods
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}
